Ternary plots for hyper2 samples

### 2023-10-29 inst/ternaryplot_hyper2.Rmd
change to include hex sticker, also cite Ternary package

---
title: "ternary_hyper2"
author: "Robin Hankin"
date: "2022-11-21"
output: html_document
---

@@

## Ternary plots for hyper2 samples

Here I show how to use the excellent `Ternary` package to generate
triangular plots for `hyper2` likelihood functions with size 3.  First
load the `Ternary` and `hyper2` packages:

@@

Above we see black circles being samples from the posterior and the
red point is the maximum likelihood estimate for the three players'
strengths.

We can adapt this technique to higher-dimensional `hyper2` objects.

>>>>

---
title: "Ternary plots for hyper2 samples"
author: "Robin Hankin"
output: html_document
bibliography: chess.bib
---

@@

```{r, label=hexstickerplotter, out.width='15%', out.extra='style="float:right; padding:10px"',echo=FALSE}
knitr::include_graphics(system.file("help/figures/hyper2.png", package = "hyper2"))
```

To cite the `hyper2` package in publications please use @hankin2017.
Here I show how to use the excellent `Ternary` package [@smith2017] to
generate triangular plots for `hyper2` likelihood functions with size
3.  First load the `Ternary` and `hyper2` packages:

@@

Above we see black circles being samples from the posterior and the
red point is the maximum likelihood estimate for the three players'
strengths.  We can adapt this technique to higher-dimensional `hyper2`
objects.
